---
title: "677hw"
author: "Kaiyu Yan"
date: "March 8, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
library(ACSWR)
library(readr)
library(sfsmisc)
```

```{r}
A <- read.delim("maybe_uniform.txt",header = F, sep= "",dec = " ")
A <-  cbind(A[1,], A[2,],A[3,],A[4,],A[5,])
A <-  as.numeric(as.vector(t(A)[,1]))
hist(A)
dist_A <- ecdf(A)
plot(dist_A)
ks.test(A,"punif")
x<-seq(-5, 5, by=0.01)
fx <- ifelse(x > 0 & x <=0.5, 3/2,
   ifelse(x > 0.5 & x < 1,  0.5, 0))
plot(x,fx)
ks.test(fx,"punif")
```
### I think the distribution of maybe_uniform belongs to uniform distribution on [0,1]. Also, there should be better fit model.


```{r}
B <- read.table("maybe_normal.txt")
B <-  cbind(B[1,], B[2,],B[3,],B[4,],B[5,],B[6,], B[7,],B[8,],B[9,],B[10,])
B <-  as.numeric(as.vector(t(B)[,1]))
qqnorm(B)
hist(B)
normal <- rnorm(1000,26,2)
hist(normal)
ks.test(B,"pnorm")
```
### According to the ks-test result, the maybe_normal belongs to normal distribution.

```{r}

C1=read.table("maybe_same_1.txt")
x=c(C1$V1,C1$V2,C1$V3,C1$V4,C1$V5)
C2=read.table("maybe_same_2.txt")
y=c(C2$V1,C2$V2,C2$V3,C2$V4,C2$V5)
ks.test(x,y)
ks.test(x+2,y)
```
### For the first question. Since p-value of of ks.test is much larger than 0.05, we cannot to reject the null hypotheses, C1,C2 are from the same distribution. Also, for the second qeustion. Since p-value of ks-test is much smaller than 0.05.Then we reject the null hypotheses, therefore C1+2 and C2 are not from the same distribution


```{r}
D <- readRDS("norm_sample.Rdata")
ks.test(D,"pnorm")
D_ecdf <- ecdf(D)
summary(D_ecdf)
plot.ecdf(D)

D_norm <- rnorm(1000)
ks.test(D,D_norm)

```


```{r}
E1 <- read.table("faithful(1).dat",header = T,skip = 25)
E2 <-  read.table("fijiquakes(1).dat",header = T)

ecdf.ksCI(E2$mag)
ecdf.ksCI(E1$waiting)
mag <- ecdf(E2$mag)
mag(4.9) - mag(4.3)

s = sd(E2$mag)
n = length(E2$mag)
error <- qt(0.95,df=n-1)*s/sqrt(n)

up <- mean(E1$waiting)+error
low <- mean(E1$waiting) -error

sprintf("The CI is %e - %e",low,up)
```